DOM Review Stats and Figures

### 2024-08-25 Analysis/ReviewFigures/Final_Figures.qmd
Big changes from ESA travel period
Added approx 30 articles, re-wrote manuscript draft

```{r load packages}
#| include: false
library(tidyverse)
library(sf)
library(readxl)
```

@@

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multispecies",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multispecies", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = fct_reorder(Taxa, Articles)) |>

@@

```{r Article coverage}
coveragePlot <- randomisationSheets |>
  summarise(N = n(), .by = c(Strata, Included)) |>
  pivot_wider(names_from = Included, values_from = N) |>
  mutate(HitRate = YES/(NO+YES)) |>
  mutate(EstRemaining = `NA`*HitRate) |>
  pivot_longer(cols = c(YES, EstRemaining), 
               names_to = 'Group', values_to = 'Articles') |>

  ggplot() +
  geom_col(aes(x = Strata, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("aquamarine4", "gray70")) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "top", axis.text = element_text(size = 12),
        axis.title = element_text(size = 12), legend.text = element_text(size = 12))

ggsave(plot = coveragePlot, "Manuscript/Figures/CoveragePlot.jpeg",
       width = 8, height = 4)
```

@@

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray80") +
  geom_sf(shape = 21,fill = "aquamarine4", colour = "white", alpha = 0.7, size = 4) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)) 
studyArea_Map
ggsave(plot = studyArea_Map, "Manuscript/Figures/StudiesMap.png")
```

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "aquamarine4") +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("0-1", "1-10", "10-100",
                              "100-\n1000", "1000-\n10000",
                              "10000-\n100000", "100000-\n1000000",
                              "1000000+")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 20,
                                   angle = 90,
                                   vjust = 1, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
studyAreaPlot

@@

```{r plot site quantity}
siteQuantityPlot <- sheet_DataCollection |>
  ggplot() +
  geom_histogram(aes(y = `Site quantity`),
                 binwidth = 0.25, fill = "aquamarine4", colour = "white") +
  geom_hline(aes(yintercept = median(`Site quantity`)), 
             colour = "goldenrod3", linetype = 2, linewidth = 2) +
  scale_y_continuous(transform = "log10",
                     limits = c(5, 10000),
                     breaks = c(10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 10000)) +
  scale_x_continuous(expand = c(0,0)) +
  labs(x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.y = element_text(size = 23),
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
siteQuantityPlot
ggsave(plot = siteQuantityPlot, filename = "Manuscript/Figures/Sites.png",
       height = 8, width = 4)
```

@@

```{r site quantity boxplots}
sheet_DataCollection |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  mutate(outlier = case_when(`Site quantity` >= 500 ~ TRUE,
                             .default = FALSE)) |>
  mutate(`Site quantity` = case_when(`Site quantity` > 500 ~ 500,
                                     .default = `Site quantity`)) |>

@@

```{r study scale over time}
sheet_DataCollection |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  filter(!`Secondary occasions` %in% c('Unclear', 'Unspecified')) |>
  separate_wider_delim(`Secondary occasions`, delim = "-",
                       names = c("minSecondary", "maxSecondary"),
                       too_few = 'align_end') |>
  mutate(maxSecondary = as.numeric(maxSecondary)) |>
  mutate(studyScale = `Site quantity`*`Primary occasions`) |>
  mutate(studyScale = case_when(studyScale > 5000 ~ 5000,
                                .default = studyScale)) |>
  mutate(outlier = case_when(studyScale >= 5000 ~ TRUE,
                             .default = FALSE)) |>

@@

```{r Objectives through time}
sheet_Objectives |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  pivot_longer(c("Demonstrate methods?", "Observe trends?", 
                 "Identify drivers?", "Test relationships?",
                 "Predict spatially?", "Predict temporally?"),
               names_to = "Objective", values_to = "ObjectiveIncluded") |>
  filter(ObjectiveIncluded == "YES") |>
  mutate(Articles = length(unique(`Review ID`)), .by = `Year Strata`) |>
  summarise(ObjArticles = n(), .by = c(Objective, Articles, `Year Strata`)) |>
  mutate(PropArticles = ObjArticles/Articles) |>
  mutate(Objective = fct_reorder(Objective, PropArticles)) |>
  complete(Objective, `Year Strata`, fill = list(PropArticles = 0)) |>
  mutate(Objective = factor(Objective, levels = c("Demonstrate methods?",
                                               "Observe trends?", 
                                               "Identify drivers?", 
                                               "Test relationships?",
                                               "Predict spatially?",
                                               "Predict temporally?"))) |>

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PropArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual(values = c("plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  labs(y = "Proportion of studies") +
  lims(y = c(0, 1)) +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "top")
```

@@

# compose table
modelling_details <- sheet_Modelling |>
  mutate(n_Overall = length(unique(`Review ID`))) |>
  mutate(n_Class = length(unique(`Review ID`)),
         .by = `Model class`) |>
  separate_longer_delim(`Performance evaluation`, ", ") |>
  separate_longer_delim(`Selection method`, ", ") |>
  mutate(GOF = case_when(`Performance evaluation` %in% c("GOF", "BayesianP") ~ TRUE,
                         .default = FALSE),
         Evaluate = case_when(`Performance evaluation` %in% c("Validation_In", "Validation_Out") ~ TRUE,
                         .default = FALSE)) |>
  mutate(Select = 1) |>
  pivot_wider(names_from = `Selection method`, 
              values_from = Select, values_fill = 0) |>
  summarise(GOF = max(GOF), Evaluate = max(Evaluate),
            `Model averaging` = max(`Model averaging`),
            `A priori` = max(`A priori`), 
            Sequential = max(Sequential), Simple = max(Simple),
            .by = c(`Review ID`, `Model class`, n_Class, n_Overall)) |>
  left_join(modelling_Covariates, by = join_by(`Review ID`))

modelling_byClass <- modelling_details |>
  summarise(Number = mean(n_Class),
            MedianCovs = median(CovsPerParam, na.rm = TRUE),
            Prop_ModAvg = sum(`Model averaging`)/mean(n_Class),
            Prop_AnySelect = 1-(sum(`A priori`)/mean(n_Class)),
            Prop_Sequential = sum(Sequential)/mean(n_Class),
            Prop_Simple = sum(Simple)/mean(n_Class),
            Prop_GOF = sum(GOF)/mean(n_Class),
            Prop_Eval = sum(Evaluate)/mean(n_Class),
            .by = `Model class`) |>
  mutate(across(where(is.numeric), ~ round(.x, 2)))

modelling_overall <- modelling_details |>
  summarise(Number = mean(n_Overall),
            MedianCovs = median(CovsPerParam, na.rm = TRUE),
            Prop_ModAvg = sum(`Model averaging`)/mean(n_Overall),
            Prop_AnySelect = 1-(sum(`A priori`)/mean(n_Overall)),
            Prop_Sequential = sum(Sequential)/mean(n_Overall),
            Prop_Simple = sum(Simple)/mean(n_Overall),
            Prop_GOF = sum(GOF)/mean(n_Overall),
            Prop_Eval = sum(Evaluate)/mean(n_Overall)) |>
  mutate(across(where(is.numeric), ~ round(.x, 2))) |>
  mutate(`Model class` = "All Models")

modelling_summary <- rbind(modelling_byClass, modelling_overall) |>
  t() |> as.data.frame()
```

>>>>

```{r load packages}
#| include: false
library(tidyverse)
library(patchwork)
library(sf)
library(readxl)
```

@@

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "VU", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multiple species",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multiple species", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = case_when(Taxa == "NA" ~ "Other", .default = Taxa)) |>
  mutate(Taxa = fct(Taxa, levels = rev(c("Bird", "Mammal", "Herptile",
                                     "Invertebrate", "Other")))) |>

@@

```{r Article coverage}
coveragePlot <- 
  randomisationSheets |>
  summarise(N = n(), .by = c(Year, Strata, Included)) |>
  pivot_wider(names_from = Included, values_from = N, values_fill = 0) |>
  mutate(HitRate = sum(YES)/(sum(NO)+sum(YES)),
         .by = Strata) |>
  mutate(EstRemaining = `NA`*HitRate) |>
  pivot_longer(cols = c(YES, EstRemaining), 
               names_to = 'Group', values_to = 'Articles') |>

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("aquamarine4", "gray70")) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "top", axis.text = element_text(size = 12),
        axis.title = element_text(size = 12), legend.text = element_text(size = 12))
coveragePlot
ggsave(plot = coveragePlot, "Manuscript/Figures/CoveragePlot.jpeg",
       width = 8, height = 4)
```

@@

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray80") +
  geom_sf(shape = 21,fill = "aquamarine4", colour = "white", alpha = 0.7, size = 2.5) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
studyArea_Map
ggsave(plot = studyArea_Map, "Manuscript/Figures/StudiesMap.png")
```

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "aquamarine4") +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("0-1", "1-10", "10-100",
                              "100-\n1000", "1000-\n10000",
                              "10000-\n100000", "100000-\n1000000",
                              "1000000+")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 20,
                                   angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
studyAreaPlot

@@

```{r plot site quantity}
siteQuantityPlot <- sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(y = `Site quantity`),
                 binwidth = 0.25, fill = "aquamarine4", colour = "white") +
  geom_hline(aes(yintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod3", linetype = 2, linewidth = 2) +
  scale_y_continuous(transform = "log10",
                     limits = c(5, 10000),
                     breaks = c(10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 10000)) +
  scale_x_continuous(expand = c(0,0)) +
  labs(x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.y = element_text(size = 23),
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
siteQuantityPlot
ggsave(plot = siteQuantityPlot, filename = "Manuscript/Figures/Sites.png",
       height = 8, width = 4)
```

@@

```{r site quantity boxplots}
sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  mutate(outlier = case_when(`Site quantity` >= 500 ~ TRUE,
                             .default = FALSE)) |>
  mutate(`Site quantity` = case_when(`Site quantity` > 500 ~ 500,
                                     .default = `Site quantity`)) |>

@@

```{r study scale over time}
sheet_DataCollection |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  filter(!`Secondary occasions` %in% c('Unclear', 'Unspecified')) |>
  separate_wider_delim(`Secondary occasions`, delim = "-",
                       names = c("minSecondary", "maxSecondary"),
                       too_few = 'align_end') |>
  mutate(maxSecondary = as.numeric(maxSecondary)) |>
  mutate(studyScale = `Site quantity`*`Primary occasions`) |>
  mutate(studyScale = case_when(studyScale > 10000 ~ 10000,
                                .default = studyScale)) |>
  mutate(outlier = case_when(studyScale >= 10000 ~ TRUE,
                             .default = FALSE)) |>

@@

```{r Objectives through time}
objectiveTrendPlot <- sheet_Objectives |>
  left_join(select(sheet_ArticleData, c(`Review ID`, `Year Strata`)), by = "Review ID") |>
  pivot_longer(c("Demonstrate methods?", "Observe trends?", 
                 "Identify drivers?", "Test relationships?",
                 "Predict spatially?", "Predict temporally?"),
               names_to = "Objective", values_to = "ObjectiveIncluded") |>
  mutate(Objective = str_replace(Objective, "\\?", "")) |>
  filter(ObjectiveIncluded == "YES") %>%
  rbind(., mutate(., `Year Strata` = "All Years")) |>
  mutate(Articles = length(unique(`Review ID`)), .by = `Year Strata`) |>
  summarise(ObjArticles = n(), .by = c(Objective, Articles, `Year Strata`)) |>
  mutate(PropArticles = (ObjArticles/Articles)*100) |>
  mutate(Objective = fct_reorder(Objective, PropArticles)) |>
  complete(Objective, `Year Strata`, fill = list(PropArticles = 0)) |>
  mutate(Strata = case_when(`Year Strata` == "All Years" ~ "left",
                            .default = "right")) |>
  mutate(Strata = fct(Strata, levels = c("left", "right"))) |>
  mutate(Objective = factor(Objective, levels = c("Demonstrate methods",
                                                  "Observe trends", 
                                                  "Identify drivers", 
                                                  "Test relationships",
                                                  "Predict spatially",
                                                  "Predict temporally"))) |>
  mutate(`Year Strata` = fct(`Year Strata`, levels = c("2004-2007",
                                                       "2008-2011",
                                                       "2012-2015", 
                                                       "2016-2019",
                                                       "2020-2023",
                                                       "All Years"))) |>

  ggplot() +
  geom_col(aes(x = `Year Strata`, y = PropArticles, fill = Objective),
           position = "dodge", colour = "white") + 
  scale_fill_manual("",
                    values = c("plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_y_continuous(breaks = c(0, 20, 40, 60, 80),
                     limits = c(0, 80),
                     labels = c("0%", "20%", "40%", "60%", "80%")) +
  labs(y = "Percentage of studies\nwith objective", x = "") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15), axis.title = element_text(size = 15),
        legend.position = "bottom", strip.background = element_blank(),
        strip.text = element_blank()) +
  facet_grid(cols = vars(Strata),
             scales = "free_x", space = "free_x", drop = TRUE)
objectiveTrendPlot
ggsave(plot = objectiveTrendPlot, "Manuscript/Figures/ObjectiveTrend.jpeg",
       width = 8, height = 4)
```

Avg covariate count by objective

```{r Objective covariate count}
covsPerParam <- sheet_Covariates |>
  separate_longer_delim(Covariates, delim = ", ") |>
  mutate(n_models = length(unique(`Model ID`)), .by = `Review ID`) |>
  filter(`Parameter type` %in% c("Initial occupancy", "Occupancy",
                                 "Colonisation", "Extinction_Persistence",
                                 "Detection")) |>
  mutate(n_params = length(unique(`Parameter type`)), .by = `Review ID`) |>
  filter(Covariates != "None") |>
  summarise(CovsPerParam = n()/(max(n_params)*max(n_models)), .by = `Review ID`)

objectiveCovariatePlot <- sheet_Objectives |>
  pivot_longer(c("Demonstrate methods?", "Observe trends?", 
                 "Identify drivers?", "Test relationships?",
                 "Predict spatially?", "Predict temporally?"),
               names_to = "Objective", values_to = "ObjectiveIncluded") |>
  mutate(Objective = str_replace(Objective, "\\?", "")) |>
  filter(ObjectiveIncluded == "YES") %>%
  rbind(., mutate(., Objective = "Any Objective")) |>
  select(`Review ID`, Objective) |>
  distinct() |>
  left_join(covsPerParam, by = join_by(`Review ID`)) |>

  mutate(Objective = factor(Objective, levels = c("Any Objective", "Demonstrate methods",
                                                  "Observe trends", 
                                                  "Identify drivers", 
                                                  "Test relationships",
                                                  "Predict spatially",
                                                  "Predict temporally"))) |>
  mutate(Objective = fct_relabel(Objective, 
                                 ~ str_replace(.x, " ", "\n"))) |>
  mutate(facet = case_when(Objective == "Any\nObjective" ~ "left",
                           .default = "right")) |>
  mutate(CovsPerParam = case_when(CovsPerParam > 10 ~ 10,
                                  .default = CovsPerParam)) |>

  ggplot(aes(x = Objective, y = CovsPerParam, 
             fill = Objective, colour = Objective)) +
  geom_boxplot(colour = "gray50", alpha = 0.6) +
  geom_jitter(alpha = 0.6, width = 0.1) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10),
                     labels = c("0", "2", "4", "6", "8", "10+")) +
  scale_fill_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                               "Observe\ntrends", "Identify\ndrivers", 
                               "Test\nrelationships", "Predict\nspatially",
                               "Predict\ntemporally"),
                    values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                               "aquamarine4", "goldenrod2", "goldenrod3")) +
  scale_colour_manual(limits = c("Any\nObjective", "Demonstrate\nmethods", 
                                 "Observe\ntrends", "Identify\ndrivers", 
                                 "Test\nrelationships", "Predict\nspatially",
                                 "Predict\ntemporally"),
                      values = c("gray60", "plum4", "cadetblue3", "aquamarine3",
                                 "aquamarine4", "goldenrod2", "goldenrod3")) +
  labs(x = "", y = "Number of covariates\nconsidered per parameter") +
  facet_grid(cols = vars(facet), scales = "free_x", space = "free_x") +
  theme(legend.position = "none",
        panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
        legend.text = element_text(size = 15), axis.text = element_text(size = 13),
        axis.title = element_text(size = 15), strip.background = element_blank(),
        strip.text = element_blank()) 
objectiveCovariatePlot
ggsave(plot = objectiveCovariatePlot, "Manuscript/Figures/ObjectiveCovariates.jpeg",
       width = 8, height = 4)
```

Combined plot

```{r combined objective plot}
stackedObjectivePlot <- objectiveTrendPlot / objectiveCovariatePlot +
   plot_annotation(tag_levels = 'A')
stackedObjectivePlot

ggsave(plot = stackedObjectivePlot, "Manuscript/Figures/ObjectiveFigure.jpeg",
       width = 12, height = 8)
```

@@

# compose table
modelling_details <- sheet_Modelling |>
  mutate(n_Overall = length(unique(`Review ID`))) |>
  mutate(n_Class = length(unique(`Review ID`)),
         .by = `Model class`) |>
  separate_longer_delim(`Performance evaluation`, ", ") |>
  separate_longer_delim(`Selection method`, ", ") |>
  mutate(GOF = case_when(`Performance evaluation` %in% c("GOF", "BayesianP") ~ TRUE,
                         .default = FALSE),
         Evaluate = case_when(`Performance evaluation` %in% c("Validation_In", "Validation_Out") ~ TRUE,
                         .default = FALSE)) |>
  mutate(Select = 1) |>
  pivot_wider(names_from = `Selection method`, 
              values_from = Select, values_fill = 0) |>
  summarise(GOF = max(GOF), Evaluate = max(Evaluate),
            `Model averaging` = max(`Model averaging`),
            `A priori` = max(`A priori`), 
            Sequential = max(Sequential), Simple = max(Simple),
            Candidate = max(`Candidate set`),
            .by = c(`Review ID`, `Model class`, n_Class, n_Overall)) |>
  left_join(modelling_Covariates, by = join_by(`Review ID`)) |>
  filter(`Model class` != "Other")

modelling_byClass <- modelling_details |>
  summarise(Number = mean(n_Class),
            MedianCovs = median(CovsPerParam, na.rm = TRUE),
            Prop_ModAvg = sum(`Model averaging`)/mean(n_Class),
            Prop_AnySelect = 1-(sum(`A priori`)/mean(n_Class)),
            Prop_Sequential = sum(Sequential)/mean(n_Class),
            Prop_Simple = sum(Simple)/mean(n_Class),
            Prop_Candidate = sum(Candidate)/mean(n_Class),
            Prop_GOF = sum(GOF)/mean(n_Class),
            Prop_Eval = sum(Evaluate)/mean(n_Class),
            .by = `Model class`) |>
  mutate(across(where(is.numeric), ~ round(.x, 2)))

modelling_overall <- modelling_details |>
  summarise(Number = mean(n_Overall),
            MedianCovs = median(CovsPerParam, na.rm = TRUE),
            Prop_ModAvg = sum(`Model averaging`)/mean(n_Overall),
            Prop_AnySelect = 1-(sum(`A priori`)/mean(n_Overall)),
            Prop_Sequential = sum(Sequential)/mean(n_Overall),
            Prop_Simple = sum(Simple)/mean(n_Overall),
            Prop_Candidate = sum(Candidate)/mean(n_Overall),
            Prop_GOF = sum(GOF)/mean(n_Overall),
            Prop_Eval = sum(Evaluate)/mean(n_Overall)) |>
  mutate(across(where(is.numeric), ~ round(.x, 2))) |>
  mutate(`Model class` = "All Models")

modelling_summary <- rbind(modelling_byClass, modelling_overall) |>
  t() |> as.data.frame() %>%
  mutate(Variable = row.names(.)) |>
  set_names(c("Frequentist", "Bayesian", "All models", "Variable")) |>
  filter(Variable != "Model class")

write_csv(modelling_summary, "Manuscript/Figures/ModellingSummary.csv")
```
